\vspace{5em}On Evaluating Adversarial Robustness

### 2019-04-25 paper.tex
Add URLs in footnotes

There are several frameworks such as CleverHans~\citep{papernot2018cleverhans} or Foolbox~\citep{rauber2017foolbox}
as well as websites\footnote{https://robust-ml.org}\textsuperscript{,}%
\footnote{https://robust.vision/benchmark/leaderboard/}\textsuperscript{,}%
\footnote{https://foolbox.readthedocs.io/en/latest/modules/zoo.html}
which have been developed to assist in this process.

@@

There are many examples of defenses building on prior work which
has since been shown to be completely broken; performing a literature
review can help avoid situations of this nature. Websites such
as \texttt{RobustML}%
\footnote{https://www.robust-ml.org/},
are explicitly designed to help track defense progress.

>>>>

There are several frameworks such as CleverHans~\citep{papernot2018cleverhans} or Foolbox~\citep{rauber2017foolbox}
as well as websites\footnote{\url{https://robust-ml.org}}\textsuperscript{,}%
\footnote{\url{https://robust.vision/benchmark/leaderboard/}}\textsuperscript{,}%
\footnote{\url{https://foolbox.readthedocs.io/en/latest/modules/zoo.html}}
which have been developed to assist in this process.

@@

There are many examples of defenses building on prior work which
has since been shown to be completely broken; performing a literature
review can help avoid situations of this nature. Websites such
as \texttt{RobustML}%
\footnote{\url{https://www.robust-ml.org/}},
are explicitly designed to help track defense progress.
